Enhancing Adversarial Robustness for Deep Metric Learning

### 2022-03-02 robdml.tex
tab
finish colorizing tab3
typofix-tab

\definecolor{cyan}{rgb}{0.0, 0.72, 0.92}

@@

To this end, Graduate Adversary, a family of pseudo-hardness functions is
proposed, which can be used as the \emph{destination} hardness.
%
A function that leads to relatively weak and relatively strong adversarial
examples, respectively in the early and late phase of training belongs to this
family.
%
As an example, we design a ``Linear Graduate Adversary'' (LGA)
function as the linearly scaled negative triplet margin, incorporating a strong
prior that the \emph{destination} hardness should remain Semihard
based on our empirical observation.

@@

% contributions
In summary, our contributions include proposing:
%
\begin{enumerate}[nosep, noitemsep, leftmargin=*]
	%
	\item {\textit{Hardness Manipulation}} (HM) as a flexible and efficient
		tool to create adversarial example triplets for subsequent adversarial
		training of a DML model.
		%
	\item \textit{Linear Gradual Adversary} (LGA) as a Graduate Adversary, \ie,
		a pseudo-hardness function for HM, which incorporates our empirical
		observations and can balance the training objectives during the
		training process.
		%
	\item \textit{Intra-Class Structure} (ICS) loss term to further improve
		model robustness and adversarial training efficiency, while such structure is
		neglected by existing defenses. 
		%
\end{enumerate}

@@

Thus, $H_\mathsf{D}$ should lead to (1) relatively weak adversarial examples in
the early training phase (indicated by a large loss value), and (2) relatively
strong adversarial examples in the late training phase (indicated by a small
loss value),
%
in order to automatically balance the training objectives (\ie, performance on
benign examples \emph{v.s.} robustness).
%
A satisfactory pseudo-hardness function is a ``Graduate Adversary''.

% Linear graduate adversary

>>>>

%TABLEAU_COLORS = {
%    'tab:blue': '#1f77b4',
%    'tab:orange': '#ff7f0e',
%    'tab:green': '#2ca02c',
%    'tab:red': '#d62728',
%    'tab:purple': '#9467bd',
%    'tab:brown': '#8c564b',
%    'tab:pink': '#e377c2',
%    'tab:olive': '#bcbd22',
%    'tab:cyan': '#17becf',
%}
\definecolor{crimson}{HTML}{DC143C}
\definecolor{tab:gray}{HTML}{7f7f7f}
\definecolor{tab:pink}{HTML}{e377c2}
\definecolor{tab:cyan}{HTML}{17becf}
\definecolor{tab:orange}{HTML}{ff7f0e}
\definecolor{tab:blue}{HTML}{1f77b4}
\definecolor{tab:red}{HTML}{d62728}

@@

To this end, Gradual Adversary, a family of pseudo-hardness functions is
proposed, which can be used as the \emph{destination} hardness.
%
A function that leads to relatively weak and relatively strong adversarial
examples, respectively in the early and late phase of training belongs to this
family.
%
As an example, we design a ``Linear Gradual Adversary'' (LGA)
function as the linearly scaled negative triplet margin, incorporating a strong
prior that the \emph{destination} hardness should remain Semihard
based on our empirical observation.

@@

% contributions
In summary, our contributions include proposing:
%
\begin{enumerate}[nosep, noitemsep, leftmargin=*]
	%
	\item {\textit{Hardness Manipulation}} (HM) as a flexible and efficient
		tool to create adversarial example triplets for subsequent adversarial
		training of a DML model.
		%
	\item \textit{Linear Gradual Adversary} (LGA) as a Gradual Adversary, \ie,
		a pseudo-hardness function for HM, which incorporates our empirical
		observations and can balance the training objectives during the
		training process.
		%
	\item \textit{Intra-Class Structure} (ICS) loss term to further improve
		model robustness and adversarial training efficiency, while such structure is
		neglected by existing defenses. 
		%
\end{enumerate}

@@

Thus, $H_\mathsf{D}$ should lead to (1) relatively weak adversarial examples in
the early training phase (indicated by a large loss value), and (2) relatively
strong adversarial examples in the late training phase (indicated by a small
loss value),
%
in order to automatically balance the training objectives (\ie, performance on
benign examples \emph{v.s.} robustness).
%
A satisfactory pseudo-hardness function is a ``Gradual Adversary''.

% Linear gradual adversary
